A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Analysis characteristics
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1074 43ef1190-90fd-4dd7-a769-d0121f02b80e

\todo{overview of characteristics and why}

>>>>

The analysis is focused on finding descriptive statistics to
understand how different servers support caching, for how long
resources hosted with those that do support caching may be considered
fresh, if it is possible to easily compute a heuristic freshness
lifetime, and revalidate the response on expiry. Apart from quoting
the numbers we aggregated, we do this by presenting summarized data
distribution visualizations, to allow for an intuitive understanding
of the data. Where appropriate, we also do statistical hypothesis
tests.
